---
title: "Power BI model details"
output: 
  html_document:
    toc: TRUE
    code_folding: hide
    toc_float:
      collapsed: FALSE
      smooth_scroll: TRUE

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(htmltools)
library(htmlwidgets)
library(RDCOMClient)
library(dplyr)
library(magrittr)
library(data.table)
library(jsonlite)
library(DT)
library(bsselectR)
library(plotly)
source('helpers.R')

dmv_queries <- fromJSON("queries/dmv.json")

# TODO: the port can be scanned from the localappdata folder
# and the initial catalog retrieved via a DMV query

con <- COMCreate("ADODB.Connection")

con[["ConnectionString"]] <- paste(
  "Provider=MSOLAP.8",
  "Integrated Security=SSPI",
  "Persist Security Info=True",
  "Data Source=localhost:59788",
  "Initial Catalog=6138de76-abee-480a-b0ed-4850117d5090",
  sep = ";")

con$Open()

```

## Initial bit

Similar to a data [dictionary structure](https://www.sciencedirect.com/topics/computer-science/data-dictionary).

### Tables {.tabset .tabset-fade}

#### List of tables
Starting with tables as they are the first thing that one sees when loading a PBIX file inside Power BI Desktop.

```{r}
tables <- get_dmv('TMSCHEMA_TABLES') %>%
  # mutate(
  #   'Local date table' = grepl('LocalDateTable[a-z0-9\\-\\_]+', Name)
  # ) %>%
  filter(
    IsHidden == 'FALSE'
  )

tables %>%
  select(
    Name,
    'Refresh policy ID' = RefreshPolicyID,
    'Excluded from refresh' = ExcludeFromModelRefresh,
    # `Local date table`
  ) %>%
  datatable(
    style = 'bootstrap4',
    filter = 'top',
    width = '775.25px')

```

#### Samples

```{r}
# Need columns in this step to add them to samples
columns <- get_dmv('TMSCHEMA_COLUMNS')
columns$ID <- as.integer(columns$ID)
columns %<>%
  arrange(ID)

samples <- tables %>% select(Name)
samples$Content <- lapply(samples$Name, get_sample)


bsselectR(samples$Name)



datatable(
  filtered_data[, "Content"],
  style = 'bootstrap4',
  filter = 'top',
  width = '775.25px'
)

```



### Partitions 

The Partition object represents a partition in a table. It is a child of a Table object and multiple partitions may be combined to form a single table. The partitions in a table define the data from external data sources that become available when the table isqueried.

```{r}

partitions <- get_dmv('TMSCHEMA_PARTITIONS')
partition_types <- fromJSON('labels/partition_types.json')
partition_modes <- fromJSON('labels/partition_modes.json')

partitions %<>%
  left_join(
    tables,
    by = c('TableID' = 'ID')
  ) %>%
  left_join(
    partition_types,
    by = c('Type' = 'ID')
  ) %>%
  left_join(
    partition_modes,
    by = c('Mode' = 'ID')
  ) %>%
  filter(
    IsHidden == 'FALSE'
  )

partitions  %>%
  select(
    'Partition name' = Name.x,
    'Table name' = Name.y,
    Description,
    'Type' = 'Type.y',
    'Mode' = 'Type.y.y',
    'Range start' = RangeStart,
    'Range end' = RangeEnd
  ) %>%
  datatable(
    style = 'bootstrap4',
    filter = 'top',
    width = '775.25px')

```

